---
title: "Week3_Assignment"
author: "Stephen Jones"
date: "February 12, 2019"
output:
  html_document:
    code_folding: hide
  pdf_document: default
---

```{r setup, include=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = TRUE)
```
3. Copy the introductory example. The vector name stores the extracted names.
R> name
[1] "Moe Szyslak" "Burns, C. Montgomery" "Rev. Timothy Lovejoy"
[4] "Ned Flanders" "Simpson, Homer" "Dr. Julius Hibbert"

```{r message=FALSE, warning=FALSE}
library(stringr)

raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
name <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))
name
```
(a) Use the tools of this chapter to rearrange the vector so that all elements conform to
the standard first_name last_name.  
Stringr was used to combine steps into a single line of code.
```{r message=FALSE, warning=FALSE}
name.fl<-str_trim(sub("([^,]+),([^,]+)","\\2 \\1", sub("[[:alpha:].]{1,3}\\. ","",name)))
cbind(name,name.fl)
```

(b) Construct a logical vector indicating whether a character has a title (i.e., Rev. and
Dr.).
```{r warning=FALSE, message=FALSE}
title<-str_detect(name,"[[:alpha:].]{2,3}\\. ")
cbind(name,title)

```

(c) Construct a logical vector indicating whether a character has a second name.  
Two answers below; the reformatted names exclude middle initial, whille the original unformatted list retains the middle initial.
```{r message=FALSE, warning=FALSE}
#derived from rearranged first_name last_name format (only checks for middle initial)
fullname<-str_detect(name.fl,"[[:alpha:].]{1}\\. ")
#derived from the original vector (only checks for middle initial)
fullname.check<-str_detect(name," [[:alpha:].]{1}\\. ")
cbind(name,fullname.check)
cbind(name.fl,fullname)
```


4. Describe the types of strings that conform to the following regular expressions and
construct an example that is matched by the regular expression.
(a) [0-9]+\\\\$
(b) \\\\b[a-z]{1,4}\\\\b
(c) .*?\\\\.txt$
(d) \\\\d{2}/\\d{2}/\\\\d{4}
(e) <(.+?)>.+?</\\\\1>

The strings "1000$"," 10$"," 45$","5.00","abcdef" are tested for (a).
```{r message=FALSE, warning=FALSE}
answer_a<-c("1000$"," 10$"," 45$","5.00","abcdef")
str_detect(answer_a,"([0-9]+\\$)")
answer_a_str<-str_c(str_extract_all(answer_a,"([0-9]+\\$)"),collapse=', ')
```
The strings "now is the time for all good peeps "," a ","four four twos ones" are tested for (b).
```{r message=FALSE, warning=FALSE}
answer_b<-c("now is the time for all good peeps "," a ","four four twos ones")
str_detect(answer_b,"\\b[a-z]{1,4}\\b")
answer_b_str<-str_c(str_extract_all(answer_b,"\\b[a-z]{1,4}\\b"),collapse=', ')
```
The strings "file.name.txt","code_2_3_2019.txt","filename","google.com" are tested for (c).
```{r message=FALSE, warning=FALSE}
answer_c<-c("file.name.txt","code_2_3_2019.txt","filename","google.com")
str_detect(answer_c,".*?\\.txt$")
answer_c_str<-str_c(str_extract_all(answer_c,".*?\\.txt$"),collapse=', ')
```
The string "11/12/2019" is tested for (d).
```{r message=FALSE, warning=FALSE}
answer_d<-"11/12/2019"
str_detect(answer_d,"\\d{2}/\\d{2}/\\d{4}")
answer_d_str<-str_c(str_extract_all(answer_d,"\\d{2}/\\d{2}/\\d{4}"),collapse=', ')
```
Strings containing HTML tags are tested for (e).
```{r message=FALSE, warning=FALSE}
answer_e<-c("<div>paragraph or graphic</div>","<p>paragraph</p>", "<div>The cat jumped over the moon. The dog quickly followed. The mouse just chilled.</div>")
str_detect(answer_e,"<(.+?)>.+?</\\1>")
answer_e_str<-str_c(str_extract_all(answer_e,"<(.+?)>.+?</\\1>"),collapse=', ')
```

Answers are combined in a dataframe and displayed using kableExtra. Backslashes are altered in knitr, so a footnote is added to explain.
```{r message=FALSE, warning=FALSE}
ex<-data.frame(example=c(answer_a_str,answer_b_str,answer_c_str,answer_d_str,answer_e_str))
ptrn<-data.frame(pattern=c("[0-9]+\\\\$","\\\\b[a-z]{1,4}\\\\b",".*?\\\\.txt$","\\\\d{2}/\\\\d{2}/\\\\d{4}","<(.+?)>.+?</\\\\1>"))
desc<-data.frame(description=c("numbers with dollar signs","words of length 1 to 4","file names ending in .txt","dates in format ##/##/####","text wrapped in html tags"))

answ_ex<-cbind(ptrn,ex,desc)
#answ_ex[1]<-NULL
answ_ex['example'] = lapply(answ_ex['example'], gsub, pattern="character[(]0[)]|c[(]|[)]|[\"]", replacement='')
answ_ex['example'] = lapply(answ_ex['example'], gsub, pattern="\\,", replacement="")

library(kableExtra)
anstable<-knitr::kable(answ_ex,"html",escape=TRUE)%>%
  kable_styling("striped",full_width = F)
anstable<-column_spec(anstable,2:3,width_max = "40em")
add_footnote(anstable, label = "Backslashes in the patterns above are actually doubled")
```
9. The following code hides a secret message. Crack it with R and regular expressions.
Hint: Some of the characters are more revealing than others! The code snippet is also
available in the materials at www.r-datacollection.com.

```{r message=FALSE,warning=FALSE}
string<-"clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0Tanwo
Uwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigO
d6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5
fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"
str_replace_all(string,"([a-z])|([0-9])|\n","")
```
